\documentclass[11pt, a4paper]{awesome-cv}

\fontdir[fonts/]
% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-skyblue}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

% Available options: circle|rectangle,edge/noedge,left/right
\name{Jakub Jan}{Duchniewicz}
\position{Senior Embedded and Software Engineer{\enskip\cdotp\enskip}Team Leader}

\email{j.duchniewicz@gmail.com}
\homepage{www.jduchniewicz.com}
\github{JDuchniewicz}
\linkedin{jduchnie}
\mobile{+48 695 671 937}

%\quote{``Success is 5\% talent and 95\% hard work"}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

\cvsection{Summary}
\newline
I am a Senior Embedded Engineer and (sometimes) a team leader at Tietoevry, specializing in developing L1 features for 5G NR on custom ASICs and designing complex systems. With an MSc in Embedded Systems and a minor in Innovation and Entrepreneurship, I bring a strong technical background and innovative mindset to my work.

My expertise spans embedded systems, FPGA, Linux, audio/video processing, game engine development, and machine learning. Proficient in C, C++, and Rust, I focus on embedded machine learning, security, and reverse engineering.

As a co-founder of Sticky Piston Studios, I innovate at the intersection of technology and creativity. I've presented at conferences such as the Embedded Open Source Summit, FOSDEM or State of Open Con, discussing AI-powered wearable health monitors and hardware acceleration using FPGAs, showcasing my frequent engagement with the tech community.

Mentoring is a passion, and I regularly share my knowledge through blog posts on my personal website. Additionally, I am an avid game jammer, consistently winning prizes for my creative and technical contributions.

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------
\input{cv/experience.tex}
\input{cv/experience.tex}
\input{cv/education.tex}
\vspace{20mm} % otherwise shitty formatting
\input{cv/extracurricular.tex}
\input{cv/presentation.tex}
\input{cv/skills.tex}
\input{cv/honors.tex}

%-------------------------------------------------------------------------------
\end{document}
