%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.Sc. in Embedded Systems} % Degree
    {EIT Digital Master School} % Institution
    {Europe} % Location
    {Sept. 2020 - Nov. 2022} % Date(s)
    {
        \begin{cvitems}
            \item { Holder of EIT Excellence Scholarship }
            \item { Winner of Digital Health Summer School with "Medpipe" - personalized tracker for recovery in endoprosthetic surgeries. }
        \end{cvitems}
    }

  \cventry
    {M.Sc. in Embedded Systems \newline FPGA accelerated packet capture with eBPF.} % Degree
    {KTH Royal Institute of Technology} % Institution
    {Stockholm, Sweden} % Location
    {Sept. 2021 - Nov. 2022} % Date(s)
    {
        \begin{cvitems}
            \item { Implemented packet capturing offload from Linux network stack to FPGA. }
            \item { Implemented Avalon MM host and target with bursting and stalling capabilities. }
            \item { Patched stmmac Ethernet driver to accelerate ingress packets on FPGA. }
            \item { Wrote userspace .pcap capturing and testing programs. }
            \item { Tested the solution using ModelSIM and SignalTap simulators. }
            \item { Achieved performance gains while maintaining power consumption. }
        \end{cvitems}
    }

  \cventry
    {M.Sc. in Embedded Systems} % Degree
    {University of Turku} % Institution
    {Turku, Finland} % Location
    {Sept. 2020 - Aug. 2021} % Date(s)
    {}


  \cventry
    {B.Sc. in Computer Science and Networks \newline FPGA based hardware accelerator for musical synthesis for Linux system.} % Degree
    {Warsaw University Of Technology} % Institution
    {Warsaw, Poland} % Location
    {Oct. 2016 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item { Nomination to IEEE Polish Diploma Contest }
          \item { Implemented DDS sythesis, filtering and sample accumulation in Verilog in a streamlined fashion. }
          \item { Implemented polyphony and various waveform shapes.}
          \item { Synchronized the programmable logic with the MCU. }
          \item { Deployed the solution in the De0 Nano SoC FPGA.}
          \item { Implemented Linux kernel drivers for communication with the FPGA and ALSA subsystem. }
          \item { Implemented the ALSA soundcard driver.}
          \item { Wrote userspace application for communicating MIDI commands to the FPGA via a kernel driver. }
          \item { Tested the solution to ensure smooth and high-fidelity sound.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
