%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Embedded and Software Engineer} % Job title
    {Tietoevry} % Organization
    {Remote - Wrocław, Poland} % Location
    {Dec. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item { Leading, supporting and coaching a team of engineers. }
          \item { Implementing 5G features on a custom ASIC modem. }
          \item { Debugging RTL and C code in Simvision. }
          \item { Converting 3GPP specification algorithms to C code. }
          \item { Development and maintenance of ORAN compliant FlexRAN fork. }
          \item { Implementation of novel ORAN features in translation module between IAPI and FAPI. }
          \item { Architected, planned and implemented L2 ORAN compliant application in C++. }
          \item { Ported FlexRAN project from icc to icx compiler. }
          \item { Fuzzing of L1-L2 interface in FlexRAN with libfuzzer. }
          \item { Debugging and fixing issues found in DPDK drivers. }
      \end{cvitems}
    }

  \cventry
    {Senior Embedded and Software Engineer} % Job title
    {Intel Corporation} % Organization
    {Remote - Wrocław, Poland} % Location
    {Jun. 2022 - Oct. 2023} % Date(s)
    {
    	\begin{cvitems}
			\item {Leading, supporting, and coaching a team of developers and managing projects.}
			\item {Recruiting engineers of all levels of expertise.}
			\item {Co-leading the ORAN M-Plane project.}
			\item {Developing the FlexRAN 5G solution.}
			\item {Implementing L1 related features.}
			\item {Implementing L2 related features.}
			\item {Conducting fuzz testing using libfuzzer and radamsa.}
			\item {Performing low-level optimization of L1 functionality.}
		\end{cvitems}
    }


	\cventry
		{Software Engineer} % Job title
		{Sticky Piston Studios} % Organization
		{Remote} % Location
		{Dec. 2020 - Present} % Date(s)
		{
			\begin{cvitems}
				\item {Developing web applications, including frontend, backend, databases, and dev ops.}
				\item {Designing UX and UI for digital products.}
				\item {Attending and participating in game jams and hackathons.}
			\end{cvitems}
		}

  \cventry
    {Embedded Software Engineer} % Job title
    {Google Summer of Code, beagleboard.org} % Organization
    {Remote} % Location
    {May. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item { Using OpenGL ES 2.0 and EGL for GPGPU computation accelerations on BeagleBone Black with SGX 5xx GPU's.}
          \item { Wrote library in C which makes these computations easier. }
          \item { Implemented most popular computations (scalar operators, array operations, 2D convolution). }
          \item { Wrote both single-shot and chain API (for combining computations). }
          \item { Benchmarked the library on various data sizes. }
          \item { Documented the project on a blog.}
      \end{cvitems}
    }

  \cventry
    {Junior Software Engineer} % Job title
    {Samsung Electronics} % Organization
    {Warsaw, Poland - Suwon, South Korea} % Location
    {Feb. 2018 - Mar. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Improved Tizen Operating System Broadcast middleware (C++/C/Arm assembly). }
        \item { Managed performance in an embedded system, through code restructurization and thread-wise code improvement.}
        \item { Improved performance of code in major broadcasting pipelining module by aware refactorization and smart usage of C++17 STL and Boost library.}
        \item { Improved overall health of code, by analysis of coredumps and various system logs. When deemed necessary provided other teams with ready solution.}
        \item { Developed from scratch a multithreaded C and C# compliant middleware process, with custom threaded work queue implementation.}
        \item { Worked with version control tools (git, p4) and in an agile environment (scrum).}
        \item { Developed bash and python scripts aiding development and analysis of problems.}
        \item { Developed python utility program for automation of defect analysis.}
        \item { Traveled to South Korea to aid with defects management during commercialization and to offer quick support.}
        \item { Worked in a diverse multi-cultural environment (directly with a group of 30 people), giving helping hand those who needed it.}
      \end{cvitems}
    }

  \cventry
    {Intern} % Job title
    {Samsung Electronics} % Organization
    {Warsaw, Poland} % Location
    {Dec. 2017 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Supported in project management and knowledge transfer from other R\&D Institute.}
        \item { Based on good performance and analytical skills got an offer for full-time work.}
      \end{cvitems}
    }

  \cventry
    {Kite/Wind/Ski Instructor} % Job title
    {BoSport/Beskid Ski Arena} % Organization
    {Chałupy/Szczyrk, Poland} % Location
    {Jun. 2014 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Worked with all kinds of people, teaching them and maintaining good relations througout the years following.}
        \item { Taught in various changing conditions, always taking responsibility for life of others.}
        \item { Taught in both Polish and English in groups up to 10 people.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
