%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
    \cventry
    {Programming and Electronics Lead} % Affiliation/role
    {Envidrawer} % Organization/group
    {Warsaw} % Location
    {Sept. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed a sustainable, automated plant growing solution working in varying climate conditions.}
        \item {Programmed a sensor-monitoring system and a visualisation web-based service.}
        \item {Designed and implemented an analog control ciruit as well as 12 V powering circuit.}
        \item {Nurtured friendly atmosphere and healthy work-life balance during the project with 2 other members.}
      \end{cvitems}
    }

    \cventry
    {Mentor} % Affiliation/role
    {BEYOND 2030 Challenge} % Organization/group
    {Turku} % Location
    {Oct. 2020 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Guided a group of 2 high-school students in their environmentally sustainable project - Smart bee-hive.}
        \item {Provided support in technical and project management matters.}
        \item {Gave support where needed, pulling the students instead of pushing.}
      \end{cvitems}
    }

    \cventry
    {Developer} % Affiliation/role
    {PolyEngine} % Organization/group
    {Warsaw}
    {Oct. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Reimplemented Entity Component System systems.}
        \item {Refactored code and cleaned architecture of engine.}
        \item {Developed various necessary features during gamejams (both gameplay and engine-wise).}
        \item {Developed 3 games during Global Game Jam 18/19 and Slavic Game Jam 18.}
        \item {Developed efficient data structures for a game engine: string and queue with STL compliance.}
      \end{cvitems}
    }
%---------------------------------------------------------
    \cventry
    {Vice President and Event Organiser} % Affiliation/role
    {KNTG Polygon} % Organization/group
    {Warsaw} % Location
    {Oct. 2017 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organised weekly meetings for student game development group Polygon.}
        \item {Gave two talks on Modern C++ usage and easily overlooked nuances.}
        \item {Planned and realised two 4-meeting editions of Game Dev Fest: invited lecturers and managed sponsorship of both events.}
        \item {Managed sponsorship funds and promotion of both events.}
        \item {Helped organise game jams (Polyjam 2018/2019).}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
