%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Honors \& Awards}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
\cvhonor
    {Award in Data for City Hackathon 2023} % Award
    {Urząd m.st. Warszawy} % Event
    {Warsaw, Poland} % Location
    {Dec. 2023} % Date(s)
\cvhonordet % ugly hack bcs i do not know tex classes lel
    {}
    {City Event Map is an innovative web and mobile application designed to uplift the quality of life for city residents. It consolidates information about local cultural events, roadworks, service interruptions, and more, simplifying information access, improving events visibility, and effectively eliminating citizens' confusion. Beyond its role as a central information hub, City Event Map acts as a vital link between municipal authorities and residents, fostering transparent and efficient communication within the community.} % Details
    {}

\cvhonor
    {Winner - Game Development Challenge} % Award
	{HackYeah} % Event
	{Kraków, Poland} % Location
	{Nov. 2022} % Date(s)
\cvhonordet % ugly hack bcs i do not know tex classes lel
	{}
	{Won the Game Development category during the largest stationary Hackathon in Europe - HackYeah. The winning game can be found here: \href{https://hist0r.itch.io/the-deluge}{The Deluge}.} % Details
	{}

  \cvhonor
    {Winner - Best Enterpreneurial Team} % Award
    {EIT Digital Summer Health SChool 2021} % Event
    {Talinn, Estonia} % Location
    {2021} % Date(s)
  \cvhonordet % ugly hack bcs i do not know tex classes lel
    {}
    {``Medpipe" - an application that will help people managing their treatment timeline and supporting materials (diet, exercises, lifestyle) before and after surgery. } % Details
    {}
    {}

  \cvhonor
    {Honorable mention} % Award
    {Warsaw Film School Game Jam VI} % Event
    {Warsaw, Poland} % Location
    {2019} % Date(s)
  \cvhonordet % ugly hack bcs i do not know tex classes lel
    {}
    {``Eternal Feud" - Low-poly, competitive co-op, made in a duo team. } % Details
    {}
    {}

  \cvhonor
    {Honorable mention} % Award
    {Static Code Analysis Competition - Samsung Electronics} % Event
    {Global} % Location
    {2018} % Date(s)

  \cvhonor
    {2nd Place Overall, 2nd Place in Innovation} % Award
    {Polyjam, Global Game Jam 2017} % Event
    {Warsaw, Poland} % Location
    {2017} % Date(s)
  \cvhonordet % ugly hack bcs i do not know tex classes lel
    {}
    {``Ommm" - Controlling a monk with the power of your voice. } % Details
    {}
    {}

%---------------------------------------------------------
\end{cvhonors}
