%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}
\begin{cventries}

	\cventry
	{Presenter for \textit{Open Source Solutions for Modern Networks}}
	{Digital Futures}
	{Warsaw, Poland}
	{May. 2024}
	{
		\begin{cvitems}
		\item {Discussed open source solutions for modern telecommunications networks, emphasizing the benefits and challenges of integrating these technologies.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Zephyr on Embedded Systems}}
	{Embedded Open Source Summit 2024}
	{Seattle, WA, USVirtualA}
	{Apr. 2024}
	{
		\begin{cvitems}
			\item {Delivered a detailed session on using Zephyr OS for embedded systems, including practical examples and case studies.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Open Source in the Development of 5G and LTE Networks}}
	{FOSDEM 2024}
	{Brussels, Belgium}
	{Feb. 2024}
	{
		\begin{cvitems}
		\item {Delivered a talk on the role of open source in 5G and LTE network development, highlighting the importance of an open ecosystem in telecommunications.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Hackaday Supercon 2023}}
	{Hackaday Supercon}
	{Pasadena, CA, USA}
	{Nov. 2023}
	{
		\begin{cvitems}
		\item {Explored creative uses of Vectorscope badges and other innovative hardware hacks.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Telco Trends and 5G Advancements}}
	{Digital Futures}
	{Kosice, Slovakia}
	{Nov. 2023}
	{
		\begin{cvitems}
		\item {Shared insights on the latest developments in 5G and their impact on daily life, showcasing Tietoevry's innovative approach.}
		\item {Provided an in-depth perspective on Telco L1, enhancing the technical discussion.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Porting an AI Powered Wearable Health Monitor to Zephyr on Open Hardware}}
	{Embedded Open Source Summit 2023}
	{Prague, Czech Republic}
	{June 2023}
	{
		\begin{cvitems}
		\item {Discussed challenges and solutions in porting AI-powered health monitors to Zephyr OS, showcasing practical insights and technical tips.}
		\end{cvitems}
	}

	\cventry
	{Presenter for \textit{Hardware Acceleration Using FPGAs in Embedded Linux}}
	{State of Open Con 2023}
	{London, United Kingdom}
	{March 2023}
	{
		\begin{cvitems}
		\item {Presented a custom Linux distribution for FPGA-based hardware acceleration, focusing on performance metrics and optimization techniques.}
		\end{cvitems}
	}
\end{cventries}
